Weighted Model Counting Without Parameter Variables

### 2021-07-09 doc/SAT_long_talk/talk.tex
Updates to talks

\begin{frame}{WMC, Formally}
  \begin{definition}
    A \alert{WMC instance} is a tuple \structure{$(\phi, X_I, X_P, w)$}, where
    \begin{itemize}
    \item \structure{$X_I$} is the set of \alert{indicator variables},
    \item \structure{$X_P$} is the set of \alert{parameter variables} (with
      \structure{$X_I \cap X_P = \emptyset$}),
    \item \structure{$\phi$} is a propositional formula in CNF over
      \structure{$X_I \cup X_P$},
    \item \structure{$w\colon X_I \cup X_P \cup \{\neg x \mid x \in X_I \cup
        X_P\} \to \mathbb{R}$} is a \alert{weight function}
      \begin{itemize}
      \item such that \structure{$w(x) = w(\neg x) = 1$} for all \structure{$x
          \in X_I$}.
      \end{itemize}
    \end{itemize}
  \end{definition}
  % \begin{definition}
  %   Let \structure{$\phi$} be a formula over a set of variables \structure{$X$}.
  %   Then \structure{$Y \subseteq X$} is a \alert{minimum-cardinality model} of
  %   \structure{$\phi$} if
  %   \begin{itemize}
  %   \item \structure{$Y \models \phi$},
  %   \item and \structure{$|Y| \le |Z|$} for all \structure{$Z \models \phi$}.
  %   \end{itemize}
  % \end{definition}
\end{frame}

% \begin{frame}{WMC and Minimum-Cardinality WMC}
%   The goal of \alert{WMC} is to compute
%   \[
%     \sum_{Y \models \phi} \prod_{Y \models l} w(l)
%   \]
%   whereas the goal of \alert{minimum-cardinality WMC} is to compute
%   \[
%     \sum_{Y \models \phi\text{, }\alert{|Y| = k}} \prod_{Y \models l} w(l),
%   \]
%   where
%   \[
%     k = \min_{Y \models \phi} |Y|.
%   \]
% \end{frame}

@@

% \begin{frame}{Additional Conditions for Minimum-Cardinality WMC}
%   \begin{itemize}
%   \item All models of \structure{$\{ c \in \phi \mid c \cap X_P = \emptyset \}$}
%     have the same number of positive indicator literals,
%   \item and
%     \[
%       \min_{Z \subseteq X_P} |Z| \quad \text{s.t. } \quad Y \cup Z \models \phi
%     \]
%     is the same for all \structure{$Y \models \{ c \in \phi \mid c \cap X_P =
%       \emptyset \}$}.
%   \end{itemize}
% \end{frame}

>>>>

\begin{frame}{WMC, Formally}
  \begin{definition}
    A \alert{WMC instance} is a tuple \structure{$(\phi, X_I, X_P, w)$}, where
    \begin{itemize}
    \item \structure{$X_I$} is the set of \alert{indicator variables},
    \item \structure{$X_P$} is the set of \alert{parameter variables} (with
      \structure{$X_I \cap X_P = \emptyset$}),
    \item \structure{$\phi$} is a propositional formula in CNF over
      \structure{$X_I \cup X_P$},
    \item \structure{$w\colon X_I \cup X_P \cup \{\neg x \mid x \in X_I \cup
        X_P\} \to \mathbb{R}$} is a \alert{weight function}
      \begin{itemize}
      \item such that \structure{$w(x) = w(\neg x) = 1$} for all \structure{$x
          \in X_I$}.
      \end{itemize}
    \end{itemize}
  \end{definition}
  \begin{definition}
    Let \structure{$\phi$} be a formula over a set of variables \structure{$X$}.
    Then \structure{$Y \subseteq X$} is a \alert{minimum-cardinality model} of
    \structure{$\phi$} if
    \begin{itemize}
    \item \structure{$Y \models \phi$},
    \item and \structure{$|Y| \le |Z|$} for all \structure{$Z \models \phi$}.
    \end{itemize}
  \end{definition}
\end{frame}

\begin{frame}{WMC and Minimum-Cardinality WMC}
  The goal of \alert{WMC} is to compute
  \[
    \sum_{Y \models \phi} \prod_{Y \models l} w(l)
  \]
  whereas the goal of \alert{minimum-cardinality WMC} is to compute
  \[
    \sum_{Y \models \phi\text{, }\alert{|Y| = k}} \prod_{Y \models l} w(l),
  \]
  where
  \[
    k = \min_{Y \models \phi} |Y|.
  \]
\end{frame}

@@

\begin{frame}{Additional Conditions for Minimum-Cardinality WMC}
  \begin{itemize}
  \item All models of \structure{$\{ c \in \phi \mid c \cap X_P = \emptyset \}$}
    have the same number of positive indicator literals,
  \item and
    \[
      \min_{Z \subseteq X_P} |Z| \quad \text{s.t. } \quad Y \cup Z \models \phi
    \]
    is the same for all \structure{$Y \models \{ c \in \phi \mid c \cap X_P =
      \emptyset \}$}.
  \end{itemize}
\end{frame}
